---
title: "UN Report on relationship between GDP and Life Expectancy"
author: "Krysta December"
date: "1/12/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse) #really only care about ggplot
```


This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r data}
gapminder_1997 <- read_csv("../data/gapminder_1997.csv")
```

```{r gdp_lifeexp_1997}
gapminder_1997 %>% 
  ggplot() +
  aes(x=gdpPercap, y=lifeExp) +
  labs(x = 'GDP per Capita', y= 'Life Expectancy', 
       title = "Do People in Wealthy Countries Live Longer?") +
  geom_point(show.legend = FALSE) +
  theme_light() +
  aes(color = continent) +
  scale_color_brewer(palette = 'Set2') +
  aes(size = pop/1000000) +
  labs (size = "Population (in millions)")
```

